A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2023-07-30 paper/fascd.tex
done

Table \ref{tab:results:classical} shows the resulting iteration counts.  For a first experiment we over-solve, with \texttt{atol} $=$ \texttt{rtol} $=$ \texttt{stol} $= 10^{-12}$ in stopping criterion \eqref{eq:stoppingcriterion}, to facilitate comparison to results in \cite[section 7]{GraeserKornhuber2009}.  As expected, RS Newton, by itself as a solver, shows rapidly-increasing iterations, roughly proportional to resolution.  By contrast, V-cycle iterations increase slowly, logarithmically with the resolution.  For the spiral problem, at fixed $m_J \approx 5.2 \times 10^5$ resolution, \cite[Figure 7.11]{GraeserKornhuber2009} reports approximately 25 V-cycle iterations for the best (truncated, TNMG/TMMG) monotone multilevel algorithms using a comparable stopping criterion.\footnote{The stopping criterion and asymptotic convergence rates in \cite{GraeserKornhuber2009} are based on norm differences from a last numerical iterate with unknown accuracy.  Our method measures accuracy directly by a residual norm, namely $\|\rSS(w)\|_2$.}  The 12 V-cycle iterations seen here from comparable resolution (8 levels) represent somewhat more arithmetic because our smoother is RS Newton using CG+IC, rather than projected Gauss-Seidel.

Resolution-dependent asymptotic convergence rates for V-cycles are shown in Figure \ref{fig:results:asymp}.  We define this rate as as $\rho_J=(\|\rSS(w^{J,k})\|_2/\|\rSS(w^{J,0})\|_2)^{1/k}$ where $w^{J,k}$ is the first iterate to satisfy \eqref{eq:stoppingcriterion}.  The complexity of the coincidence set or free boundary does not appear to strongly influence FASCD V-cycle performance, as both iterations and rates are similar for the ball and spiral problems.  Contrast the rate of about $0.1$ for 8 levels with about $0.4$ reported by \cite[Figure 7.11]{GraeserKornhuber2009} for TNMG/TMMG at comparable resolution.  These rates are all excellent, and our better rate mostly reflects a stronger smoother.

For F-cycles we instead used \texttt{rtol} $= 10^{-8}$, sufficient to reach discretization error, and we report the number of V-cycles after the ramp.  A small, constant number of cycles apparently solves the problem.  However, spiral needs more V-cycles to clean-up error remaining after the ramp, presumably from the initial-iterate injection scheme during the ramp (Section \ref{sec:implementation}).  Since each V-cycle does the work of about eight finest-level Krylov iterations, the ball results show nearly textbook multigrid efficiency at the highest resolutions despite the low solution regularity.
\end{example}

>>>>

Table \ref{tab:results:classical} shows the resulting iteration counts.  For a first experiment we over-solve, with \texttt{atol} $=$ \texttt{rtol} $=$ \texttt{stol} $= 10^{-12}$ in stopping criterion \eqref{eq:stoppingcriterion}, to facilitate comparison to results in \cite[section 7]{GraeserKornhuber2009}.  As expected, RS Newton as a solver shows rapidly-increasing iterations, roughly proportional to resolution.  By contrast, V-cycle iterations increase slowly, perhaps logarithmically with the resolution.  For the spiral problem, \cite[Figure 7.11]{GraeserKornhuber2009} reports that a $m_J \approx 5.2 \times 10^5$ problem needs approximately 25 V-cycle iterations for the best (truncated, TNMG/TMMG) monotone multilevel algorithms.\footnote{The stopping criterion and asymptotic convergence rates in \cite{GraeserKornhuber2009} are based on norm differences from a last numerical iterate with unknown accuracy.  Our method measures accuracy directly by a residual norm, namely $\|\rSS(w)\|_2$.}  The 12 V-cycle iterations needed here, at comparable resolution (8 levels), represent somewhat more arithmetic because our smoother is RS Newton using CG+IC, rather than projected Gauss-Seidel.  Resolution-dependent asymptotic convergence rates for V-cycles, defined as $\rho_J=(\|\rSS(w^{J,k})\|_2/\|\rSS(w^{J,0})\|_2)^{1/k}$ where $w^{J,k}$ is the first iterate to satisfy \eqref{eq:stoppingcriterion}, are shown in Figure \ref{fig:results:asymp}.  Both iterations and rates are similar for the ball and spiral problems suggesting that the geometric complexity of the coincidence set and free boundary minimally influences FASCD V-cycle performance.  (The highest-resolution rate difference has no explanation for now.)  Contrast the rate of about $0.1$ for 8 levels here with about $0.4$ reported by \cite[Figure 7.11]{GraeserKornhuber2009} for TNMG/TMMG at comparable resolution.  These rates are all excellent; our better rate mostly reflects a stronger smoother.

For F-cycles we instead used the defaults \texttt{rtol} $=$ \texttt{stol} $= 10^{-8}$, sufficient to reach discretization error, and in Table \ref{tab:results:classical} we report the number of V-cycles after the ramp; a small, constant number solves the problem.  Since each V-cycle does the work of about eight finest-level Krylov iterations, the ball results show nearly textbook multigrid efficiency at the highest resolutions despite the low solution regularity.  More V-cycles are needed to clean-up error remaining after the ramp in the spiral problem, presumably from the F-cycle initial-iterate injection scheme (Section \ref{sec:implementation}).
\end{example}
